{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-04-28 draft.tex
Precision and Success Figures are Added for UAV123 and OTB100
Cleaned up the introduction.

\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and extends amsmath package
\usepackage{algorithm}		% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
\usepackage{comment, url}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications for embedded systems in that most of the embedded systems
already includes image acquisition pipeline and a tremendous amount of
progresses on research has been made for many areas. However, to
successfully deploy a computer vision algorithm on any existing
embedded systems, a vision algorithm needs to satisfy some criteria:
minimal, manual intervention after deployment and small footprint of
computing resource consumption and on executable code, with the
assumption of reasonably good performance. To this end, in this paper,
we propose an ensemble of the kernelized correlation filters (KCF), we
call {\it E}nKCF, for a single-target object tracking. In particular,
we developed a committee of KCFs to specifically address the
scale-change and dynamic maneuver of the target over frames. In
addition, we devised a Bayes filter for a smooth transition between
individual KCFs' executions. To minimize the effect of drifting, we
also developed another algorithm that detects target-lost, uses an
existing object proposal method (e.g., ``Edge Box'') to re-detect the
lost target, and re-initializes the previous tracking for a long-term
tracking. To verify the usefulness of the proposed method, we compared
the performance of ours to those of the existing online tracking
methods. Experimental results showed that the performance of ours are
72.53\% for precision on 20 pixels and 52.90\% for success rate for
OTB100 data, and 55.71\% and 41.71\% for UAV123 data. These results
confirmed that our method outperformed the existing ones over 5\% on
precision on 20 pixels and 10-20\% on AUC on average. Our
implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
DCF (457 fps), and STC (350 fps) for UAV123.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\begin{itemize}
\item YoungWoo: Clean up the introduction
\item Burak: Clean up the technical section: EnKCF, KCF, and Particle Filter
\item Burak: You'll have a conclusion whether we'll have the re-detection part by Friday night.
\item By Monday, we'll have a draft ready to submit.
\end{itemize}

A recent proliferation of air/ground/water unmanned vehicle
technologies has ever increased interests on deployment of intelligent
algorithms on embedded or mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because those mobile platforms have limited payload to carry other
active sensors than a lightweight, monocular camera and, without
increasing much cost, installation of a monocular camera even stereo
rigs would increase the usefulness of a mobile platform. For example,
instead of having just bare flight function with video recording, an
unmanned air vehicle (UAV) equipped with object or feature following
would make it more useful in the application of
monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

In this paper, we propose a single-target tracking that aims at
running on any embedded or mobile platforms that doesn't require an
offline training, and can run on an embedded system. In particular, we
would like to make our algorithm 1) learn the appearance model of a
target on the fly and 2) run as fast on a typical desktop as up to
300Hz so that it could run up to 30Hz when it is deployed on a
low-end, embedded system. With these features, our tracking algorithm
is ready to track an object of interest when it is deployed on an
embedded system. To this end, an online object tracking is more
appropriate.

{\it We may need to change this introductory sentence based on the
  results.}

One of the dominant frameworks for online object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that the target location is given at the very first
image frame like other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a circulant matrix
\cite{henriques2015high}. One can optimally solve this regression
problem using a ridge regression in a closed form. However, such a
solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter provides one with a much
cheaper solution, $\mathcal{O}(n\log n)$ over element-wise
multiplication in a frequecny domain
\cite{bolme2010visual,henriques2015high}. Thank to this reformulation,
a complete pipeline of an object tracker based on the correlation
filter can be easily implemented and run very efficiently in an online
fashion. In fact, a variant of the correlation filter, kernelized
correlation filter with multi-channel features, outperformed other
state-of-the-art tracking algorithms in VOT15 challenge, in terms of
run-time and tracking accuracy. However, the vanilla form of such an
online tracker is prone to drift, and fails to track a target over a
long period of time primarily \cite{henriques2015high} because of the
dilemma of stability-plasticity in updating appearance model, where
the appearance model will be overfitted to only the images used to
train and a compromise on the frequency of updating the model is
carefully implemented \cite{santner2010prost}. For example, a naive
way of handling a scale change of a target could reduce the run-time
performance from 300 to 100 fps. A seemingly obvious way of addressing
the scale change is to scan the region of interest (ROI) with
templates in different dimensions based on pre-defined scale ratios to
find the target
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
because of computational nature of correlation filter, this approach
would just increase the computational complexity of tracking by
running detection with multiple possibilities.

Another way of handling the scale change for the correlation filter
based approach is to find a correct scale at a location where a target
highly likely appears \cite{zhang2014fast}. In particular, they uses
the MOSSE tracker to estimate a target's translation. The scale is
updated in a naive way where the confidence map is used to determine
the scale change between successive frames.

For instance, their method assumes similar scale in between two
consecutive frames given similar confidences. With this simple method,
we do not need to run detection on different ROIs at a given frame and
perform tracking at $\geq300$ fps. In this study, we propose the use
of Ensemble KCFs in an intuitive way to perform robust scale-adaptive
tracking at more than $300$ fps. Our approach is inspired by
\cite{ma2015long} where two KCFs are employed as translation and scale
filters. It first estimates translation using the translation filter
learned on \textit{target}$+$\textit{background} area. Then, the scale
filter learned on the \textit{target} area is used to estimate new
scale of the target at the estimated position. Application of
translation and scale filter at each frame reduces run-time
performance ($\leq50 fps$) as we need to run detection on each scale
candidate and perform training on both filters. Similarly, we learn
three different correlation filters specializing on different aspects
of tracking and addresses the weakness of each other, resulting in
more robust tracking. We name these filters as
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). Unlike \cite{ma2015long}, by running a single filter at
each frame, we can achieve the targeted operation frame rate. The
fig.~\ref{fig:Filters} shows the size of the ROIs associated with
$R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$ in addition to the hanning
windows assigned and desired Gaussian responses assigned to each one.

The recent progress on development of convolutional neural networks
(CNN) is astonishing as since the AlexNet \cite{krizhevsky12} broke
the record for the ImageNet competition, at every year, new and better
results are reported. Moreover, there have been many attempts to
deploy CNN on the mobile devices
\cite{wu2016quantized,giusti2015}. But the inherent limitation of such
a supervised learning based object tracking is that an either online
\cite{nam2016} or offline \cite{held2016} training tracker has to be
prior to deploy the algorithm.

@@

>>>>

\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and extends amsmath package
\usepackage{algorithm}		% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
\usepackage{comment, url}
\usepackage{subcaption}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications for embedded systems. This is primarily because most of
the embedded systems already includes image acquisition pipeline and a
tremendous amount of progresses on research has been made for many
areas in computer vision. However, to successfully deploy a computer
vision algorithm on any existing embedded systems, a vision algorithm
needs to satisfy some criteria: minimal, manual intervention after
deployment and small footprint of computing resource consumption and
on executable code, with the assumption of reasonably good
performance. To this end, in this paper, we propose an ensemble of the
kernelized correlation filters (KCF), we call {\it E}nKCF, for a
single-target object tracking. In particular, we developed a committee
of KCFs to specifically address the scale-change and dynamic maneuver
of the target over frames. In addition, we devised a Bayes filter for
a smooth transition between individual KCFs' executions. To minimize
the effect of drifting, we also developed another algorithm that
detects target-lost, uses an existing object proposal method (e.g.,
``Edge Box'') to re-detect the lost target, and re-initializes the
previous tracking for a long-term tracking. To verify the usefulness
of the proposed method, we compared the performance of ours to those
of the existing online tracking methods. Experimental results showed
that the performance of ours are 72.53\% for precision on 20 pixels
and 52.90\% for success rate for OTB100 data, and 55.71\% and 41.71\%
for UAV123 data. These results confirmed that our method outperformed
the existing ones over 5\% on precision on 20 pixels and 10-20\% on
AUC on average. Our implementation ran at 340 fps for OTB100 and at
416 fps for UAV123 data that is faster than DCF (292 fps) for OTB100
and KCF (292 fps), DCF (457 fps), and STC (350 fps) for UAV123.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\begin{comment}
\begin{itemize}
\item YoungWoo: Clean up the introduction
\item Burak: Clean up the technical section: EnKCF, KCF, and Particle Filter
\item Burak: You'll have a conclusion whether we'll have the re-detection part by Friday night.
\item By Monday, we'll have a draft ready to submit.
\end{itemize}
\end{comment}
A recent proliferation of air/ground/water unmanned vehicle
technologies has ever increased interests on deployment of intelligent
algorithms on embedded or mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because payloads of those mobile platforms are limited to carry other
sensors than a lightweight or an array of monocular cameras. For
example, instead of having just bare flight function with video
recording, an unmanned air vehicle (UAV) equipped with object or
feature following would make it more useful in the application of
monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

In this paper, we propose a single-target tracking that aims at
running on any embedded or mobile platforms that doesn't require an
offline training, and can run on an embedded system. In particular, we
would like to make our algorithm 1) learn the appearance model of a
target on the fly and 2) run as fast on a typical desktop as up to
400Hz so that it could run up to 40Hz when it is deployed on a
low-end, embedded system. With these features, our tracking algorithm
is ready to track an object of interest when it is deployed on an
embedded system. To this end, an online object tracking is more
appropriate.

One of the dominant frameworks for online object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that the target location is given at the very first
image frame like other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a circulant matrix
\cite{henriques2015high}. One can optimally solve this regression
problem using a ridge regression in a closed form. However, such a
solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequecny domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, a complete pipeline of an object tracker based on
the correlation filter can be easily implemented and run very
efficiently in an online fashion. In fact, a variant of the
correlation filter, kernelized correlation filter with multi-channel
features, outperformed other state-of-the-art tracking algorithms in
VOT15 challenge, in terms of run-time and tracking accuracy. However,
the vanilla form of such an online tracker is prone to drift, and
fails to track a target over a long period of time primarily
\cite{henriques2015high} because of the dilemma of
stability-plasticity in updating appearance model, where the
appearance model will be overfitted to only the images used to train
and a compromise on the frequency of updating the model is carefully
implemented \cite{santner2010prost}. For example, a naive way of
handling a scale change of a target could reduce the run-time
performance from 300 to 100 fps. A seemingly obvious way of addressing
the scale change is to scan the region of interest (ROI) with
templates in different dimensions based on pre-defined scale ratios to
find the target
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
because of computational nature of correlation filter, this approach
would merely increase the computational complexity of tracking by
running detection with multiple templates.

Another way of handling the scale change for the correlation filter
based approach is to find a correct scale at a location where a target
highly likely appears \cite{zhang2014fast}. In particular, they uses
the MOSSE tracker to estimate a target's translation. The scale is
updated in a way where the confidence map is used to determine the
scale change between successive frames. This is because they assumes
the scale of a target wouldn't change much over two consecutive
frames. Similarly \cite{ma2015long} used two KCFs to learn the
translation and scale of a target separately. To more specific, a KCF
is used to learn the translation of the target and its
background. Given this, another KCF is used to learn the target area
to estimate a new scale of the target. However, because of running
more than a KCF on each frame, this method degrades its run-time
performance (i.e., $\leq 50 fps$). Our method is motivated by this
idea -- the idea of deploying multiple KCFs to address the issues of
single target tracking: scale and translation. In this paper, we use
an ensemble of KCFs in turn, instead of running them all together on
every frame. By doing so, we could still address the scale change and
estimate target's motion efficiently while increasing run-time
performance. In particular, we deploy three KCF in turn:
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). Figure \ref{fig:Filters} shows examples of the ROIs
associated with $R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$.
\begin{comment}
{\it We may not need this.}
The recent progress on development of convolutional neural networks
(CNN) is astonishing as since the AlexNet \cite{krizhevsky12} broke
the record for the ImageNet competition, at every year, new and better
results are reported. Moreover, there have been many attempts to
deploy CNN on the mobile devices
\cite{wu2016quantized,giusti2015}. But the inherent limitation of such
a supervised learning based object tracking is that an either online
\cite{nam2016} or offline \cite{held2016} training tracker has to be
prior to deploy the algorithm.
\end{comment}

@@

\begin{figure}
        \begin{subfigure}[b]{0.25\textwidth}
                \includegraphics[width=\linewidth]{./figures/Precision_UAV123.pdf}
        \end{subfigure}%
        \begin{subfigure}[b]{0.25\textwidth}
                \includegraphics[width=\linewidth]{./figures/Success_UAV123.pdf}
        \end{subfigure}%
        \caption{Pictures of animals}\label{fig:animals}
\end{figure}

\begin{figure}
        \begin{subfigure}[b]{0.25\textwidth}
                \includegraphics[width=\linewidth]{./figures/Precision_OTB100.pdf}
        \end{subfigure}%
        \begin{subfigure}[b]{0.25\textwidth}
                \includegraphics[width=\linewidth]{./figures/Success_OTB100.pdf}
        \end{subfigure}%
        \caption{Pictures of animals}\label{fig:animals}
\end{figure}
